|

### 2023-02-01 paper.Rmd
Wed Feb  1 12:00:06 CET 2023: update-remote.sh

@@

The first interesting observation from this experiment is, that the pre-trained DAE-GP shows slightly lower mean RMSE (higher fitness) but a higher median RMSE (lower fitness) than regular DAE-GP for both the training and the testing set in overall fitness.Regarding the presence of overfitting, both DAE-GP variants show only a very small gap between the testing and training fitness which indicates a good generalization behavior.

@@

@@

# Values are copied from file /eda-gp-2020/experiments/airfoil_2hl_150hn_fullRun_30gens/airfoil_2hl_150hn_fullRun_30gens_TimeBenchmark.ipynb

REG_TIME <- 5076.448
PT_TIME <- 14706.465
PT_TIME_NOPT <- 12536.889

REG_MEDIAN_EPOCHSTRAINED <- 122.0
PT_MEDIAN_EPOCHSTRAINED <- 53.5

REG_MEDIAN_SAMPLINGTIME <- 29.055806166997172
PT_MEDIAN_SAMPLINGTIME <- 198.4502993219976

REG_TIME_NOSAMLING <-  3550.276852743067
PT_TIME_NOSAMPLING  <- 8705.007590330817
PT_TIME_NOSAMPLING_NOPT  <- 6622.027293765

@@

Suprisingly, even after correcting the runtime for both DAE-GP results by removing the time spend during sampling, my implementation of pre-training for DAE-GP still on average takes more time to finish the search process as shown in figure \@ref(fig:airfoil-runtime-noSampling-total). While traditional DAE-GP has a median runtime without sampling time of `r format(REG_TIME_NOSAMLING, scientific=F)` seconds , the runtime of pre-trained DAE-GP, without time for samling and pre-training, still increases by a factor of `r round(PT_TIME_NOSAMPLING_NOPT / REG_TIME_NOSAMLING, 3)` to `r format(PT_TIME_NOSAMPLING_NOPT, scientific=F)` seconds.

>>>>

```{python read_runtime_vars, echo=FALSE}
from json import load
D_AIRFOIL_2hl = load(
  open("/Users/rmn/github/master_thesis/data/airfoil_2hl_150hn_fullRun_30gens/summary.json", "r", encoding="utf-8")
  )

D_AIRFOIL_1hl = load(
  open("/Users/rmn/github/master_thesis/data/airfoil_1hl_150hn_fullRun_30gens/summary.json", "r", encoding="utf-8")
  )

REG_TRAIN_MED_FF <- py$D_AIRFOIL_2hl$REG_TRAIN_MED_FF
REG_TEST_MED_FF <- py$D_AIRFOIL_2hl$REG_TEST_MED_FF
PT_TRAIN_MED_FF <- py$D_AIRFOIL_2hl$PT_TRAIN_MED_FF
PT_TEST_MED_FF <- py$D_AIRFOIL_2hl$PT_TEST_MED_FF
GP_TRAIN_MED_FF <- py$D_AIRFOIL_2hl$GP_TRAIN_MED_FF
GP_TEST_MED_FF <- py$D_AIRFOIL_2hl$GP_TEST_MED_FF
REG_TRAIN_STDD_FF <- py$D_AIRFOIL_2hl$REG_TRAIN_STDD_FF
REG_TEST_STDD_FF <- py$D_AIRFOIL_2hl$REG_TEST_STDD_FF
PT_TRAIN_STDD_FF <- py$D_AIRFOIL_2hl$PT_TRAIN_STDD_FF
PT_TEST_STDD_FF <- py$D_AIRFOIL_2hl$PT_TEST_STDD_FF
GP_TRAIN_STDD_FF <- py$D_AIRFOIL_2hl$GP_TRAIN_STDD_FF
GP_TEST_STDD_FF <- py$D_AIRFOIL_2hl$GP_TEST_STDD_FF

REG_TRAIN_MED_FF_1HL <- py$D_AIRFOIL_1hl$REG_TRAIN_MED_FF
REG_TEST_MED_FF_1HL <- py$D_AIRFOIL_1hl$REG_TEST_MED_FF
PT_TRAIN_MED_FF_1HL <- py$D_AIRFOIL_1hl$PT_TRAIN_MED_FF
PT_TEST_MED_FF_1HL <- py$D_AIRFOIL_1hl$PT_TEST_MED_FF
GP_TRAIN_MED_FF_1HL <- py$D_AIRFOIL_1hl$GP_TRAIN_MED_FF
GP_TEST_MED_FF_1HL <- py$D_AIRFOIL_1hl$GP_TEST_MED_FF
REG_TRAIN_STDD_FF_1HL <- py$D_AIRFOIL_1hl$REG_TRAIN_STDD_FF
REG_TEST_STDD_FF_1HL <- py$D_AIRFOIL_1hl$REG_TEST_STDD_FF
PT_TRAIN_STDD_FF_1HL <- py$D_AIRFOIL_1hl$PT_TRAIN_STDD_FF
PT_TEST_STDD_FF_1HL <- py$D_AIRFOIL_1hl$PT_TEST_STDD_FF
GP_TRAIN_STDD_FF_1HL <- py$D_AIRFOIL_1hl$GP_TRAIN_STDD_FF
GP_TEST_STDD_FF_1HL <- py$D_AIRFOIL_1hl$GP_TEST_STDD_FF

@@

The first interesting observation from this experiment is, that the pre-trained DAE-GP shows slightly lower mean RMSE of `r round(, 3)` (higher fitness) but a higher median RMSE (lower fitness) than regular DAE-GP for both the training and the testing set in overall fitness. Regarding the presence of overfitting, both DAE-GP variants show only a very small gap between the testing and training fitness which indicates a good generalization behavior.

@@

```{python read_runtime_vars, echo=FALSE}
from json import load
D_AIRFOIL_TIME = load(
  open("/Users/rmn/github/master_thesis/data/airfoil_2hl_150hn_fullRun_30gens_TimeBenchmark/summary.json", "r", encoding="utf-8")
  )
```

@@

REG_TIME <- py$D_AIRFOIL_TIME$REG_TIME
PT_TIME <- py$D_AIRFOIL_TIME$PT_TIME
PT_TIME_NOPT <- py$D_AIRFOIL_TIME$PT_TIME_NOPT

REG_MEDIAN_EPOCHSTRAINED <- py$D_AIRFOIL_TIME$REG_MEDIAN_EPOCHSTRAINED
PT_MEDIAN_EPOCHSTRAINED <- py$D_AIRFOIL_TIME$PT_MEDIAN_EPOCHSTRAINED

REG_MEDIAN_SAMPLINGTIME <- py$D_AIRFOIL_TIME$REG_MEDIAN_SAMPLINGTIME
PT_MEDIAN_SAMPLINGTIME <- py$D_AIRFOIL_TIME$PT_MEDIAN_SAMPLINGTIME

REG_TIME_NOSAMLING <-  py$D_AIRFOIL_TIME$REG_TIME_NOSAMLING
PT_TIME_NOSAMPLING  <- py$D_AIRFOIL_TIME$PT_TIME_NOSAMPLING
PT_TIME_NOSAMPLING_NOPT  <- py$D_AIRFOIL_TIME$PT_TIME_NOSAMPLING_NOPT

REG_PARAMS <- py$D_AIRFOIL_TIME$REG_PARAMS
PT_PARAMS <- py$D_AIRFOIL_TIME$PT_PARAMS

@@

Suprisingly, even after correcting the runtime for both DAE-GP results by removing the time spend during sampling, my implementation of pre-training for DAE-GP still on average takes more time to finish the search process as shown in figure \@ref(fig:airfoil-runtime-noSampling-total). While traditional DAE-GP has a median runtime without sampling time of `r format(REG_TIME_NOSAMLING, scientific=F)` seconds , the runtime of pre-trained DAE-GP, without time for samling and pre-training, still increases by a factor of `r round(PT_TIME_NOSAMPLING_NOPT / REG_TIME_NOSAMLING, 3)` to `r format(PT_TIME_NOSAMPLING_NOPT, scientific=F)` seconds. While investigating other reasons for the differences in runtime, I verified that both DAE-GP variants use the exact same number of trainable parameters for each generations DAE-LSTMS models ( `r format(REG_PRAMS, scientific=F)`).
